Governing through patronage: the bargain for education in decentralized Brazil

### 2020-09-11 paper/paper.tex
finished version paper

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/plot_coalition_coef_mun.pdf}
    \caption{{\bf Political alignment and staff turnover.} An increase in the share of legislative seats held by the mayoral coalition decrease the amount of turnover for teachers and school principals, including hires or dismissals. Model 1 presents results on the turnover index. Models 2 and 3 are logistic regressions at the individual, bureaucrat level. Models 4 and 5 are aggregated at the municipal level. where the outcome of interest is the proportion of staff either hired or dismissed at a given year. Models 1, 3, and 5 include year and state fixed effects.}
    \label{fig:coalition_turnover}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/plot_coalition_coef_mun_second.pdf}
    \caption{\textbf{Patronage continues into the second term.} All models include a full set of controls, as well as year and state fixed effects.}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/plot_coalition_coef_mun.pdf}
    \caption{{\bf Political alignment and staff turnover.} A visual representation of results presented in table \ref{tbl:turnover}. All models include year and state fixed effects.}
    \label{fig:coalition_turnover}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/plot_coalition_coef_mun_second.pdf}
    \caption{\textbf{Patronage continues into the second term.} There is strong evidence that executive-legislative bargains continue into the mayor's second term. All models include a full set of controls, as well as year and state fixed effects.}
\end{figure}
